On Math

### 2025-04-28 cards/paper.tex
euler on polyhedrons and linear regression + linear correlation coef

\section{Displacement}
\begin{equation}
  s = ut+\frac{1}{2}gt^2
\end{equation}
where:

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Midpoint} & \textbf{F*M} & \textbf{$M_i * \overline{\rm x}$} & \textbf{($M_i - \overline{\rm x})^2$} & \textbf{$f_i * (M_i - \overline{\rm x})$} \\
\hline
$10$ & $50$ & $-31.333$ & $981.776$ & $4908.879$ \\
\hline
$10$ & $30$ & $-11.333$ & $128.444$ & $1284.437$ \\
\hline
$50$ & $400$ & $8.667$ & $75.112$ & $600.894$ \\
\hline
$70$ & $490$ & $28.667$ & $821.780$ & $5752.458$  \\
\hline
\end{tabular}
\caption{Not sure what to type in here}
\label{tab:estimating_a_mean_and_variance_3}
\end{table}
\begin{equation}
  \begin{gathered}
    \sigma^2_n \approx \frac{4908... + 1284... + 600... + 5752}{30} \approx 418.2  \\
    \sigma_n \approx \sqrt{418.2} \approx 20.5
  \end{gathered}
\end{equation}
\subsection{Sum of squares}
Given that variance is:
\begin{equation}
  \sigma^2_x = \frac{1}{n} \sum_{i=1}^n(x_i - \overline{\rm x})^2
\end{equation}
The sum of squares is the same but with no fraction:
\begin{equation}
  S_{xx} = \sum_{i=1}^n(x_i - \overline{\rm x})^2
\end{equation}
Compare covariance with a sum of squares:
\begin{equation}
  \begin{gathered}
    Cov(x,y) = \frac{1}{n} \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y}) \\
    S_{xy} = \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y})
  \end{gathered}
\end{equation}
Variance and covariance in terms of $S_{xx}$, $S_{yy}$ and $S_{xy}$:
\begin{equation}
  \begin{gathered}
    \sigma^2_x = \frac{S_{xx}}{n} \\
    \sigma^2_y = \frac{S_{yy}}{n} \\
    Cov(x,y) = \frac{S_{xy}}{n}
  \end{gathered}
\end{equation}
%TODO: some heading?
Shortcut formulas:
\begin{equation}
  \begin{gathered}
    S_{xx} = \sum_{i=1}^n x_i^2 - \frac{1}{n} (\sum_{i=1}^n x_i)^2 \\
    S_{yy} = \sum_{i=1}^n y_i^2 - \frac{1}{n} (\sum_{i=1}^n y_i)^2 \\
    S_{xy} = \sum_{i=1}^n x_iy_i - \frac{1}{n} (\sum_{i=1}^n x_i)(\sum_{i=1}^n y_i)
  \end{gathered}
\end{equation}
\subsection{Linear coefficient}
Signed with $\rho$ (Greek letter called 'rho').
- $\rho = 1$ means perfect positive correlation
- $\rho = -1$ means perfect negative correlation
- $\rho = 0$ no (linear) correlation
\section{Logarithms}
\begin{table}[htbp]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Property} & \textbf{Formula} \\
\hline
Product Rule & $\log_a(xy) = \log_a(x) + \log_a(y)$ \\
\hline
Quotient Rule & $\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ \\
\hline
Power Rule & $\log_a(x^n) = n \cdot \log_a(x)$ \\
\hline
Change of Base & $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ \\
\hline
Equating arguments & $\log_af(x) = log_ag(x)$ is the same as $f(x) = g(x)$ \\
\hline
\end{tabular}
\caption{Fundamental Properties of Logarithms}
\label{tab:log_properties}
\end{table}

>>>>

\subsection{Euler on polyhedrons}
A polyhedron is \textbf{convex} if and only if the following condition
holds:
If we take any two distinct points A and B that belong to the polyhedron
then all the points on the line segment AB also belong to the polyhedron.

Euler's formula for polyhedra for any convex polyhedron, the following
relationship must be satisfied.
\begin{equation}
  V - E + F = 2
\end{equation}

$V$ - number of vertices

$E$ - number of edges

$F$ - number of faces

The \textbf{Euler characteristic} of any polyhedra is denoted by the
Greek letter $\aleph$ (``k-eye'') and is equal to the number:
\begin{equation}
  \aleph = V - E + F
\end{equation}
Any convex polyhedron has
\begin{equation}
  \aleph = 2
\end{equation}
\section{Displacement}
\begin{equation}
  s = ut+\frac{1}{2}gt^2
\end{equation}
where:

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Midpoint} & \textbf{F*M} & \textbf{$M_i * \overline{\rm x}$} & \textbf{($M_i - \overline{\rm x})^2$} & \textbf{$f_i * (M_i - \overline{\rm x})$} \\
\hline
$10$ & $50$ & $-31.333$ & $981.776$ & $4908.879$ \\
\hline
$10$ & $30$ & $-11.333$ & $128.444$ & $1284.437$ \\
\hline
$50$ & $400$ & $8.667$ & $75.112$ & $600.894$ \\
\hline
$70$ & $490$ & $28.667$ & $821.780$ & $5752.458$  \\
\hline
\end{tabular}
\caption{Not sure what to type in here}
\label{tab:estimating_a_mean_and_variance_3}
\end{table}
\begin{equation}
  \begin{gathered}
    \sigma^2_n \approx \frac{4908... + 1284... + 600... + 5752}{30} \approx 418.2  \\
    \sigma_n \approx \sqrt{418.2} \approx 20.5
  \end{gathered}
\end{equation}
\subsection{Sum of squares}
Given that variance is:
\begin{equation}
  \sigma^2_x = \frac{1}{n} \sum_{i=1}^n(x_i - \overline{\rm x})^2
\end{equation}
The sum of squares is the same but with no fraction:
\begin{equation}
  S_{xx} = \sum_{i=1}^n(x_i - \overline{\rm x})^2
\end{equation}
Compare covariance with a sum of squares:
\begin{equation}
  \begin{gathered}
    Cov(x,y) = \frac{1}{n} \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y}) \\
    S_{xy} = \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y})
  \end{gathered}
\end{equation}
Variance and covariance in terms of $S_{xx}$, $S_{yy}$ and $S_{xy}$:
\begin{equation}
  \begin{gathered}
    \sigma^2_x = \frac{S_{xx}}{n} \\
    \sigma^2_y = \frac{S_{yy}}{n} \\
    Cov(x,y) = \frac{S_{xy}}{n}
  \end{gathered}
\end{equation}
%TODO: some heading?
Shortcut formulas:
\begin{equation}
  \begin{gathered}
    S_{xx} = \sum_{i=1}^n x_i^2 - \frac{1}{n} (\sum_{i=1}^n x_i)^2 \\
    S_{yy} = \sum_{i=1}^n y_i^2 - \frac{1}{n} (\sum_{i=1}^n y_i)^2 \\
    S_{xy} = \sum_{i=1}^n x_iy_i - \frac{1}{n} (\sum_{i=1}^n x_i)(\sum_{i=1}^n y_i)
  \end{gathered}
\end{equation}
\subsection{Linear regression}
For a set of $n$ paired observations $x_i$ and $y_i$ the trend line is the
straight line that best fits the data.
Finding the equation of the trend line is called \textbf{linear regression}
or best fit.
We can show that the equation of the trend line is given by:
\begin{equation}
  y = mx * b
\end{equation}
1. Slope $m$
\begin{equation}
  m = \frac{S_{xy}}{S_{xx}}
\end{equation}
2. y-intercept - b:
\begin{equation}
  b = \overline{\rm y} - m\overline{\rm x}
\end{equation}
3. $\overline{\rm x}$ and $\overline{\rm y}$ are the means of the data sets:
\begin{equation}
  \overline{\rm x} = \frac{1}{n} \sum_{i=1}^nx_i, \overline{\rm y} = \frac{1}{n} \sum_{i=1}^ny_i,
\end{equation}
4. quantities $S_{xx}$ and $S_{xy}$:
\begin{equation}
  \begin{gathered}
    S_{xx} = \sum_{i=1}^n (x_i - \overline{\rm x})^2 \\
    S_{xy} = \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y})
  \end{gathered}
\end{equation}
There is some nice intuition behind the formula for $b$. The trend line
always passes through the point $(\overline{\rm x}, \overline{\rm y})$.
Therefore, this point must satisfy the trend line equation:
\begin{equation}
  y = mx + b
\end{equation}
We can then solve this equation for $b$. Also notice that $S_{xx}$ and $S_{xy}$
are the summation terms that feature in the formulas for the variance and
covariance respectively.
\subsection{Linear coefficient}
Signed with $\rho$ (Greek letter called 'rho').
- $\rho = 1$ means perfect positive correlation
- $\rho = -1$ means perfect negative correlation
- $\rho = 0$ no (linear) correlation
\subsection{Linear correlation coefficient}
$|p| > 0.7$ - correlation is strong
$0.3 \leqslant |p| \leqslant 0.7$ - correlation is weak
$0 \leqslant |p| \leqslant 0.3$ - correlation is negligible
\subsection{Linear correlation coefficient using sigma notation}
\begin{equation}
  p = \frac{S_{xy}}{\sqrt{S_{xx} * S_{yy}}}
\end{equation}
\section{Logarithms}
\begin{table}[htbp]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Property} & \textbf{Formula} \\
\hline
Product Rule & $\log_a(xy) = \log_a(x) + \log_a(y)$ \\
\hline
Quotient Rule & $\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ \\
\hline
Power Rule & $\log_a(x^n) = n \cdot \log_a(x)$ \\
\hline
Change of Base & $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ \\
\hline
Equating arguments & $\log_af(x) = log_ag(x)$ is the same as $f(x) = g(x)$ \\
\hline
\end{tabular}
\caption{Fundamental Properties of Logarithms}
\label{tab:log_properties}
\end{table}
